The proof equivalence problem for multiplicative linear logic is \textsc{pspace}-complete\\[4pt]\large Abstract

### 2013-09-30 LIX colloquium/Extended abstract.tex
Add reference to extended abstract

\linespread{1.1}\selectfont
\noindent\emph{\MLL\ proof equivalence} is the problem of deciding whether one proof in multiplicative linear logic may be turned into another by a series of commuting conversions. It is also the \emph{word problem} for $\star$-autonomous categories \citep{Barr-1991}: the problem of deciding whether two term representations denote the same morphism in any $\star$-autonomous category. In \MLL$^{-}$, without the two units, proof equivalence corresponds to syntactic equality on \emph{proof nets} \citep{Girard87, DR89}, and is linear-time decidable. For full \MLL, thanks to many years of work on proof nets \citep{TrimbleThesis, BCST, HughesFreeStar} we know that the proof equivalence problem corresponds to a reasonably simple graph-rewiring problem.

>>>>

\linespread{1.1}\selectfont
\noindent\emph{\MLL\ proof equivalence} is the problem of deciding whether one proof in multiplicative linear logic may be turned into another by a series of commuting conversions. It is also the \emph{word problem} for $\star$-autonomous categories \citep{Barr-1991}: the problem of deciding whether two term representations denote the same morphism in any $\star$-autonomous category. In \MLL$^{-}$, without the two units, proof equivalence corresponds to syntactic equality on \emph{proof nets} \citep{Girard87, DR89}, and is linear-time decidable. For full \MLL, thanks to many years of work on proof nets \citep{TrimbleThesis, BCST, Strassburger-Lamarche-2004, HughesFreeStar} we know that the proof equivalence problem corresponds to a reasonably simple graph-rewiring problem.
